Generating Images From Captions\\ With Attention

### 2015-10-31 iclr-paper-new.tex
update model description

\section{Model}
Our proposed model 
defines a generative process of images conditioned on captions. In particular, captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on a canvas $c_t$ over time $t=1,...,T$. Our model can be viewed as a part of the sequence-to-sequence framework \citep{ilya_mt,cho_mt,nitish_video}.
%Our proposed model can be viewed as a part of sequence-to-sequence framework \citep{ilya_mt}, \citep{cho_mt}, \citep{nitish_video} where captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on canvas over time $t=1,...,T$. Let $\icaption$ be the input caption, consisting of $N$ words $y_{1}, y_{2}, ..., y_{n}$ and $\oimage$ be the image corresponding to that caption.

@@

\begin{figure}[t!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\includegraphics[width=0.99\textwidth]{figures/alignDrawAnnotated.pdf}\quad
%
\end{center}
\caption{The image of the proposed model}
\label{fig:figmodel}
\vspace{-0.3cm}
\end{figure}

>>>>

\section{Model}
\label{sec:model}
Our proposed model 
defines a generative process of images conditioned on captions. In particular, captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on a canvas $c_t$ over time $t=1,...,T$. Our model can be viewed as a part of the sequence-to-sequence framework \citep{ilya_mt,cho_mt,nitish_video}.
%Our proposed model can be viewed as a part of sequence-to-sequence framework \citep{ilya_mt}, \citep{cho_mt}, \citep{nitish_video} where captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on canvas over time $t=1,...,T$. Let $\icaption$ be the input caption, consisting of $N$ words $y_{1}, y_{2}, ..., y_{n}$ and $\oimage$ be the image corresponding to that caption.

@@

\begin{figure}[t!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\includegraphics[width=0.99\textwidth]{figures/alignDrawAnnotated.pdf}\quad
%
\end{center}
\caption{The diagram shows our model learns to draw images by learning an alignment of input captions and generating canvas. The details are explained in Section \ref{sec:model}.}
\label{fig:figmodel}
\vspace{-0.3cm}
\end{figure}
